Enhance Road Detection Data Processing of LiDAR Point Clouds to Specifically Identify Unmarked Gravel Rural Roads

### 2023-02-25 Huston_Paper.tex
Logic for simple ensemble

	{Of the algorithms tested (Appendix \ref{apdx:Appendix_2}), the RDF that used RANSAC as the plane projection method and the full feature set seemed to perform the most consistently for true non-road surface identification. While it did struggle with gravel identification (32.72\% average accuracy) with a high confusion rate with grass (27.47\% false identification), there was a consistent decrease ($>20\%$) in false-positive road identification in side-of-road areas. }

	{It was found that while none of the algorithms excelled in all areas, }

	\begin{table}[H]
		\centering
		\begin{tblr}{width=0.9\linewidth,colspec={|Q[1,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|}}
			\hline
			Algorithm & Average \% of True Gravel Type & Average \% of True Chipseal Type & Average \% of True Surface Type Identification & Average \% True Road Surface Detection & Average \% of True  Non-Road Surface Detection\\
			\hline
			MLS ALL & 27.35 & 61.50 & 46.59 & 82.90 & 55.01 \\
			\hline
			MLS TT  & 27.62 & 50.37 & 40.86 & 89.44 & 37.31 \\
			\hline
			ZXY     & 31.70 & 65.65 & 50.60 & 93.15 & 55.16 \\
			\hline
			RAN ALL & 32.72 & 48.42 & 42.38 & 56.25 & 66.50 \\
			\hline
			RANGE   & 56.92 & 39.97 & 51.61 & 78.53 & 47.92 \\
			\hline
			RAN TT  & 82.84 & 27.60 & 57.29 & 65.32 & 58.51 \\
			\hline
		\end{tblr}
		\caption[Averaged Results]{Average results for all algorithms and all tested roads}
		\label{tab:averaged_results}
	\end{table}

>>>>

	{It was found that while none of the algorithms excelled in all areas, the results seem to indicate that implementing a multiple-model algorithm to create an ensemble would greatly increase road detection accuracy. Of the algorithms tested (Appendix \ref{apdx:Appendix_2}), the RDF that used RANSAC as the plane projection method and the full feature (designated RAN ALL) performed the most consistently for true non-road surface identification, with an average of 66.5\% (median of 65.5\%). While it did struggle with gravel identification (32.72\% average accuracy) with a high confusion rate with grass (27.47\% false identification), it may be supplemented with the RDF designated RANGE, which has the highest true-positive gravel identification rate of 82.8\%. A classification method was tested to verify this method based on RAN ALL and RANGE algorithms. RAN ALL would would designate non-road surfaces and the determination of road surface type was a combined effort of the two (Figure \ref{}), thus achieving a higher accuracy. }

	\begin{table}[H]
		\centering
		\begin{tblr}{width=0.9\linewidth,colspec={|Q[1,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|Q[1.5,m,c]|}}
			\hline
			Algorithm Designation & Average \% of True Gravel Type Identification & Average \% of True Chipseal Type Identification & Average \% of True Surface Type Identification & Average \% True Road Surface Detection & Average \% of True  Non-Road Surface Detection\\
			\hline
			MLS ALL & 35.354 & 68.581 & 46.587 & 82.896 & 55.006 \\
			\hline
			MLS TT  & 37.833 & 55.162 & 40.865 & 89.444 & 37.308 \\
			\hline
			ZXY     & 35.697 & 73.211 & 50.601 & 93.153 & 55.156 \\
			\hline
			RAN ALL & 36.119 & 54.169 & 42.376 & 56.252 & 66.500 \\
			\hline
			RANGE   & 61.822 & 44.758 & 51.610 & 78.526 & 47.918 \\
			\hline
			RAN TT  & 54.508 & 27.617 & 57.293 & 65.323 & 58.506 \\
			\hline
%			Ens\_1  & 61.822 & 44.758 & 51.610 & 78.526 & 66.685 \\
%			\hline
		\end{tblr}
		\caption[Averaged Results]{Average results of all algorithms on tested roads. }
		\label{tab:averaged_results}
	\end{table}

%	\begin{figure}[H]
%		\centering
%		\includegraphics[width=0.75\linewidth]{figures/RAN_ALL_ofroad_RANGE_onroad}
%		\caption[Early Stopping]{Diminishing returns on increasing algorithm size versus accuracy can be used to determine the early stopping point of algorithm growth.}
%		\label{fig:combo_result}
%	\end{figure}
